Towards topological type theory for decrypting transfinite methods in classical mathematics

### 2025-08-25 slides-ai2025.tex
More work on the slides

  \begin{mining}[0.85\textwidth]
    \textbf{Scholium
    \fixedhref{https://www2.mathematik.tu-darmstadt.de/~kohlenbach/inconsistentfeasibility.pdf}{[Kohlenbach
    2018]}.} In this situation, let~$b$ be an upper bound on the norm of~$x$ and let~$K$ be an
    upper bound for the norm of~$N$ arbitrary points $c_i \in C_i$. Then
    \[ \forall \varepsilon > 0\_
      \forall n \geq \phi(\varepsilon,N,b,K)\_
      \|T^{n+1}x - T^nx\| < \varepsilon, \]
    where~$\phi(\varepsilon,N,b,K)$ is given by a certain explicit formula.
  \end{mining}
\end{frame}

@@

@@

- Start:

  - classical logic fairy tale?
  - overview as in Swansea talk

- A glimpse of proof mining
  - Euclid proof
  - Gauß proof
  - Successes of proof mining in diverse fields
  - Example: running Euclid

@@

>>>>

  \begin{mining}[0.85\textwidth]
    \textbf{Scholium
    \fixedhref{https://www2.mathematik.tu-darmstadt.de/~kohlenbach/inconsistentfeasibility.pdf}{[Kohlenbach
    2018]}.} In this situation, let~$b$ be an upper bound on the norm of~$x$ and let~$K$ be an
    upper bound on the norm of~$N$ arbitrary points $c_i \in C_i$. Then
    \[ \forall \varepsilon > 0\_
      \forall n \geq \phi(\varepsilon,N,b,K)\_
      \|T^{n+1}x - T^nx\| < \varepsilon, \]
    where~$\phi(\varepsilon,N,b,K)$ is given by a certain explicit formula.
  \end{mining}
\end{frame}

@@

\begin{frame}{Backed by logical metatheorems?}
  \hil{Metatheorems} have been and are being developed which \ldots
  \begin{enumerate}
    \item guarantee the \hil{extractability} of suitable numerical information in principle
    (bounds on norms, convergence rates, moduli of uniqueness, rates of
    asymptotic regularity, \ldots),
    \item describe an \hil{algorithm} for carrying out the extraction and
    \item support \hil{modular treatments} of auxiliary lemmas,
  \end{enumerate}
  \bad{\textbf{provided}} the input proof is supplied in a
  certain \hil{formal system}.

  NB: The \hil{quality} of the extracted data depends on the
  \hil{sophistication} of the \hil{logical~principles} used in the proof
  (Heine--Borel, Bolzano--Weierstraß, \ldots).

  \bad{\textbf{In practice (2025):}} Algorithms \bad{\textbf{not}} used, only followed
  as \bad{\textbf{rough guidelines}}, combined with hand-rolled optimizations.
\end{frame}

@@

- Start:
  - classical logic fairy tale?
  - overview as in Swansea talk

- A glimpse of proof mining
  - Euclid proof
  - Euler proof
  - Successes of proof mining in diverse fields
  - Example: running Euclid

@@

- formulation problem
- infinite objects
- proving = programming
